---
title: "DATA EXPLORATION PROJECT"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## LOADING NECCESSARY PACKAGES

```{r pack ,echo=TRUE}
library(tidyverse)
library(vtable)
library(jtools)
library(readr)
library(purrr)
library(dplyr)
library(plyr)


```


## READING DATA AND DATA CLEANING

After loading the data sets from Lab3_rawdata, we must perform some data evaluations like looking at the data summary and structure. Moreover, the data must be cleaned for it to be used in analysis later on.

```{r data, echo=TRUE}
# Reading most+recent+cohorts+(scorecard + elements).csv


scorecard <- read.csv("Lab3_Rawdata/Most+Recent+Cohorts+(Scorecard+Elements).csv")
summary(scorecard)


# Reading id_name_link csv
name_link<- read.csv("Lab3_Rawdata/id_name_link.csv")

summary(name_link)



# Joining the scorecard data to the name link data
SCORECARD_LINKED<-scorecard %>% full_join(name_link, by = c("UNITID" = "unitid"),keep=TRUE)

summary(SCORECARD_LINKED)

str(SCORECARD_LINKED)

#Reading the google trend datasets
trends1<-read.csv("Lab3_Rawdata/trends_up_to_inter_1.csv")

trends2<-read.csv("Lab3_Rawdata/trends_up_to_inter_2.csv")

trends3<-read.csv("Lab3_Rawdata/trends_up_to_inter_3.csv")

trends4<-read.csv("Lab3_Rawdata/trends_up_to_inter_4.csv")

trends5<-read.csv("Lab3_Rawdata/trends_up_to_inter_5.csv")

trends6<-read.csv("Lab3_Rawdata/trends_up_to_inter_6.csv")

trendsUM<-read.csv("Lab3_Rawdata/trends_up_to_UM.csv")

trendsPHOENIX<-read.csv("Lab3_Rawdata/trends_up_to_UPhoenix.csv")

trendsUT<-read.csv("Lab3_Rawdata/trends_up_to_UT.csv")

trendsUTMB<-read.csv("Lab3_Rawdata/trends_up_to_UTMB.csv")

trendsYORK<-read.csv("Lab3_Rawdata/trends_up_to_Yorktowne.csv")

trendsFINISH<-read.csv("Lab3_Rawdata/trends_up_to_finish.csv")
# Merging the trend data sets into one data frame
trends1$rn<-rownames(trends1)

trends2$rn<-rownames(trends2)

trends3$rn<-rownames(trends3)

trends4$rn<-rownames(trends4)

trends5$rn<-rownames(trends5)

trends6$rn<-rownames(trends6)

trendsUM$rn<-rownames(trendsUM)

trendsPHOENIX$rn<-rownames(trendsPHOENIX)

trendsUT$rn<-rownames(trendsUT)

trendsUTMB$rn<-rownames(trendsUTMB)

trendsYORK$rn<-rownames(trendsYORK)

trendsFINISH$rn<-rownames(trendsFINISH)

GOOGLE_TREND<-join_all(list(trends1,trends2,trends3,trends4,trends5,trends6,trendsUM,trendsPHOENIX,trendsUTMB,trendsYORK,trendsFINISH),by="rn",type="full")

summary(GOOGLE_TREND)



# Joining the scorecard dataframe with the google trend dataframe

SCORECARD_trend<-SCORECARD_LINKED %>% inner_join(GOOGLE_TREND, by = "schname",keep=TRUE)

# Dropping universities with duplicate school names

SCORECARD_trends<-SCORECARD_trend %>% distinct(schname.x,schname.y, .keep_all = TRUE)

```


# Regression analysis

The variables that we have picked to evaluate if the high earnings or low earning college is the cost NPT4_PUB.AVERAGE.ANNUAL.COST and the md_earn_wne_p10.REPORTED.EARNINGS as this gives us a chance to look at education as an investment. This will clearly show the universities with the highest Return on investments and if the high ROI translates to a higher trend index on google.


```{r analy,echo=TRUE, echo=TRUE}
lmindex<- lm(index~md_earn_wne_p10.REPORTED.EARNINGS + NPT4_PUB.AVERAGE.ANNUAL.COST,data = SCORECARD_trends)
summary(lmindex)
```

From the above regression, the pvalues that have been generated are way too large as compared to 0.05. This is an indication of a no relation between the high income colleges with the google trend index.
this can be reinforced when we have a look at the residues which basically should be nearing zero for the fit and arguement of having a significate relation between the google trend index and the income of colleges.



# Adding a regression plot 

```{r plot, echo=TRUE}
plot(SCORECARD_trends$index,pch = 16, col = "blue")
abline(lmindex)

```

This plot reinforces our the results that have being given by the regression analysis above. we can conculsively say that the income of colleges rarely affects the google trend index.


